---
title: "Fall 2021 Survey"
subtitle: "Nittany Amateur Radio Club"
output: 
  html_document:
    self_contained: false
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

# Purpose

This document imports, cleans, and summarizes data from the Fall 2021 NARC member survey.

# Outline

1. Import the data from Google.
2. Clean and reformat.
3. Visualize.

# Set-up

```{r}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "img/",
  dev = "png",
  dpi = 300,
  fig.align = "center",
  fig.width = 7,
  fig.height = 3
)
```

## Install required packages

```{r}
if (!require(tidyverse)) {
  install.packages('tidyverse')
  library(tidyverse) # for pipe `%>%`
}

if (!require(googledrive)) {
  install.packages('googledrive')
}
```

## Authenticate to Google

Since the survey data are in a Google sheet, we need to authenticate to Google to retrieve them. The following code chunk should *not* be run interactively.

```{r, eval = FALSE}
# The survey results are in a file called `NARC Fall 2021 Member Survey (Responses)`.
googledrive::drive_download(file = 'NARC Fall 2021 Member Survey (Responses)', path = 'csv/narc-fall-2021-survey', type = 'csv', overwrite = TRUE)
```

# Import & Clean

The earlier step downloaded the data to `csv/narc-fall-2021-survey.csv`.

```{r}
narc_fall_2021 <- readr::read_csv("csv/narc-fall-2021-survey.csv")
```
We'll rename some of the variables to make them easier to deal with.

```{r}
narc_fall_2021_vhf <- narc_fall_2021 %>%
  dplyr::rename(., packet_exp = 'Please describe your level of experience with the following VHF/UHF digital modes. [VHF packet]',
                aprs_exp = "Please describe your level of experience with the following VHF/UHF digital modes. [APRS]",
                winlink_exp = "Please describe your level of experience with the following VHF/UHF digital modes. [Winlink]",
                fldigi_exp = "Please describe your level of experience with the following VHF/UHF digital modes. [Fldigi]",
                ft8_exp = "Please describe your level of experience with the following VHF/UHF digital modes. [FT8 and related modes]",
                packet_interest = "Describe your level of interest in the following VHF/UHF digital modes. [VHF packet]",
                aprs_interest = "Describe your level of interest in the following VHF/UHF digital modes. [APRS]",
                winlink_interest = "Describe your level of interest in the following VHF/UHF digital modes. [Winlink]",
                fldigi_interest = "Describe your level of interest in the following VHF/UHF digital modes. [Fldigi]",
                ft8_interest = "Describe your level of interest in the following VHF/UHF digital modes. [FT8 and related modes]",
                atv_exp = "Describe your level of experience with the following VHF/UHF operations. [Amateur TV]",
                aredn_exp = "Describe your level of experience with the following VHF/UHF operations. [AREDN  (& related networking)]",
                digital_voice_exp = "Describe your level of experience with the following VHF/UHF operations. [FM digital voice (e.g. Allstar, DMR, D-STAR)]",
                cw_exp = "Describe your level of experience with the following VHF/UHF operations. [CW]",
                contesting_exp = "Describe your level of experience with the following VHF/UHF operations. [Contesting]",
                satellite_interest = "Describe your level of interest in the following VHF/UHF operations. [Satellite]",
                atv_interest = "Describe your level of interest in the following VHF/UHF operations. [Amateur TV]",
                aredn_interest = "Describe your level of interest in the following VHF/UHF operations. [AREDN (& related networking)]",
                digital_voice_interest = "Describe your level of interest in the following VHF/UHF operations. [FM digital voice (e.g., Allstar, DMR, D-STAR)]",
                cw_interest = "Describe your level of interest in the following VHF/UHF operations. [CW]",
                contesting_interest = "Describe your level of interest in the following VHF/UHF operations. [Contesting]",
                satellite_exp = "Describe your level of experience with the following VHF/UHF operations. [Satellite]",
                follow_up = "The survey is anonymous unless you want to identify yourself. If you identify yourself, we may want to follow up with you. So, if you want to be contacted for follow-up, please give us your name, callsign, and the best way to reach you (email/phone)."
                ) %>%
  dplyr::select(., packet_exp, packet_interest,
                aprs_exp, aprs_interest,
                winlink_exp, winlink_interest,
                ft8_exp, ft8_interest,
                fldigi_exp, fldigi_interest,
                atv_exp, atv_interest,
                cw_exp, cw_interest,
                contesting_exp, contesting_interest,
                aredn_exp, aredn_interest,
                satellite_exp, satellite_interest,
                digital_voice_exp, digital_voice_interest)
```

## Mountaintop station activities

```{r}
narc_fall_2021_mtn <- narc_fall_2021 %>%
  dplyr::rename(., have_keys = "Do you have keys to the mountaintop station?",
                last_visit = "When was the last time you visited the station?",
                participated_in = "If you have visited in the last 3 years, what activities did you participate in?",
                didnt_visit_because = "If you have _not_ visited the station, why not?",
                would_participate_in = "If the club offered the following activities at the mountaintop, which would you participate in?",
                other_thoughts = "Any other thoughts on how the mountaintop station fits into your plans for ham radio now or in the near future?") %>%
  dplyr::select(., have_keys, last_visit, participated_in, didnt_visit_because, would_participate_in,
                other_thoughts)
```

# Visualize results for modes/operating

Rick is experimenting with the `likert` package. Here is a reference:

https://jakec007.github.io/2021-06-23-R-likert/

## Packet

```{r}
packet <- narc_fall_2021_vhf %>%
  dplyr::select(., packet_exp, packet_interest) %>%
  dplyr::mutate(., packet_exp = factor(packet_exp, 
                                       levels = c("Never tried", "Tried 1-2 times", "Use rarely", "Use occasionally", "Use regularly")),
                packet_interest = factor(packet_interest,
                                         levels = c("Not interested", "Potentially interested", "Interested", "Very interested"))) %>%
  dplyr::rename("Experience with packet" = packet_exp,
                "Interest in packet" = packet_interest)

packet <- data.frame(packet)
```

```{r packet_exp}
plot(likert::likert(packet[, 1, drop = FALSE]), legend.position = "right")
```

```{r packet_int}
plot(likert::likert(packet[, 2, drop = FALSE]), legend.position = "right")
```

## APRS

```{r}
aprs <- narc_fall_2021_vhf %>%
  dplyr::select(., aprs_exp, aprs_interest) %>%
  dplyr::mutate(
    .,
    aprs_exp = factor(
      aprs_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    aprs_interest = factor(
      aprs_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with APRS" = aprs_exp,
                "Interest in APRS" = aprs_interest)

aprs <- data.frame(aprs)
```

```{r aprs_exp}
plot(likert::likert(aprs[, 1, drop = FALSE]), legend.position = "right")
```

```{r aprs_int}
plot(likert::likert(aprs[, 2, drop = FALSE]), legend.position = "right")
```

## Winlink

```{r}
winlink <- narc_fall_2021_vhf %>%
  dplyr::select(., winlink_exp, winlink_interest) %>%
  dplyr::mutate(
    .,
    winlink_exp = factor(
      winlink_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    winlink_interest = factor(
      winlink_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with Winlink" = winlink_exp,
                "Interest in Winlink" = winlink_interest)

winlink <- data.frame(winlink)
```

```{r winlink_exp}
plot(likert::likert(winlink[, 1, drop = FALSE]), legend.position = "right")
```

```{r winlink_int}
plot(likert::likert(winlink[, 2, drop = FALSE]), legend.position = "right")
```

## fldigi

```{r}
fldigi <- narc_fall_2021_vhf %>%
  dplyr::select(., fldigi_exp, fldigi_interest) %>%
  dplyr::mutate(
    .,
    fldigi_exp = factor(
      fldigi_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    fldigi_interest = factor(
      fldigi_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with fldigi" = fldigi_exp,
                "Interest in fldigi" = fldigi_interest)

fldigi <- data.frame(fldigi)

```

```{r fldigi_exp}
plot(likert::likert(fldigi[, 1, drop = FALSE]), legend.position = "right")
```

```{r fldigi_int}
plot(likert::likert(fldigi[, 2, drop = FALSE]), legend.position = "right")
```

## FT8

```{r}
ft8 <- narc_fall_2021_vhf %>%
  dplyr::select(., ft8_exp, ft8_interest) %>%
  dplyr::mutate(
    .,
    ft8_exp = factor(
      ft8_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    ft8_interest = factor(
      ft8_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with FT8" = ft8_exp,
                "Interest in FT8" = ft8_interest)

ft8 <- data.frame(ft8)
```


```{r ft8_exp}
plot(likert::likert(ft8[, 1, drop = FALSE]), legend.position = "right")
```

```{r ft8_int}
plot(likert::likert(ft8[, 2, drop = FALSE]), legend.position = "right")
```

## ATV

```{r}
atv <- narc_fall_2021_vhf %>%
  dplyr::select(., atv_exp, atv_interest) %>%
  dplyr::mutate(
    .,
    atv_exp = factor(
      atv_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    atv_interest = factor(
      atv_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with ATV" = atv_exp,
                "Interest in ATV" = atv_interest)

atv <- data.frame(atv)
```


```{r atv_exp}
plot(likert::likert(atv[, 1, drop = FALSE]), legend.position = "right")
```

```{r atv_int}
plot(likert::likert(atv[, 2, drop = FALSE]), legend.position = "right")
```

## AREDN

```{r}
aredn <- narc_fall_2021_vhf %>%
  dplyr::select(., aredn_exp, aredn_interest) %>%
  dplyr::mutate(
    .,
    aredn_exp = factor(
      aredn_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    aredn_interest = factor(
      aredn_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with AREDN" = aredn_exp,
                "Interest in AREDN" = aredn_interest)

aredn <- data.frame(aredn)
```

```{r aredn_exp}
plot(likert::likert(aredn[, 1, drop = FALSE]), legend.position = "right")
```


```{r aredn_int}
plot(likert::likert(aredn[, 2, drop = FALSE]), legend.position = "right")
```

## CW

```{r}
cw <- narc_fall_2021_vhf %>%
  dplyr::select(., cw_exp, cw_interest) %>%
  dplyr::mutate(
    .,
    cw_exp = factor(
      cw_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    cw_interest = factor(
      cw_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with CW" = cw_exp,
                "Interest in CW" = cw_interest)

cw <- data.frame(cw)

```

```{r cw_exp}
plot(likert::likert(cw[, 1, drop = FALSE]), legend.position = "right")
```

```{r cw_int}
plot(likert::likert(cw[, 2, drop = FALSE]), legend.position = "right")
```

## Digital voice

```{r}
digital_voice <- narc_fall_2021_vhf %>%
  dplyr::select(., digital_voice_exp, digital_voice_interest) %>%
  dplyr::mutate(
    .,
    digital_voice_exp = factor(
      digital_voice_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    digital_voice_interest = factor(
      digital_voice_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with digital voice" = digital_voice_exp,
                "Interest in digital voice" = digital_voice_interest)

digital_voice <- data.frame(digital_voice)
```

```{r digital_voice_exp}
plot(likert::likert(digital_voice[, 1, drop = FALSE]), legend.position = "right")
```

```{r digital_voice_int}
plot(likert::likert(digital_voice[, 2, drop = FALSE]), legend.position = "right")
```

## Contesting

```{r}
contesting <- narc_fall_2021_vhf %>%
  dplyr::select(., contesting_exp, contesting_interest) %>%
  dplyr::mutate(
    .,
    contesting_exp = factor(
      contesting_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    contesting_interest = factor(
      contesting_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with contesting" = contesting_exp,
                "Interest in contesting" = contesting_interest)

contesting <- data.frame(contesting)
```

```{r contesting_exp}
plot(likert::likert(contesting[, 1, drop = FALSE]), legend.position = "right")
```

```{r contesting_int}
plot(likert::likert(contesting[, 2, drop = FALSE]), legend.position = "right")
```

## Satellite

```{r}
satellite <- narc_fall_2021_vhf %>%
  dplyr::select(., satellite_exp, satellite_interest) %>%
  dplyr::mutate(
    .,
    satellite_exp = factor(
      satellite_exp,
      levels = c(
        "Never tried",
        "Tried 1-2 times",
        "Use rarely",
        "Use occasionally",
        "Use regularly"
      )
    ),
    satellite_interest = factor(
      satellite_interest,
      levels = c(
        "Not interested",
        "Potentially interested",
        "Interested",
        "Very interested"
      )
    )
  ) %>%
  dplyr::rename("Experience with satellite ops" = satellite_exp,
                "Interest in satellite ops" = satellite_interest)

satellite <- data.frame(satellite)
```

```{r satellite_exp}
plot(likert::likert(satellite[, 1, drop = FALSE]), legend.position = "right")
```

```{r satellite_int}
plot(likert::likert(satellite[, 2, drop = FALSE]), legend.position = "right")
```

# Visualize results for mountaintop use

## Have keys

```{r}
have_keys_df <- narc_fall_2021_mtn %>%
  dplyr::select(., have_keys) %>%
  dplyr::mutate(
    .,
    have_keys = factor(
      have_keys,
      levels = c(
        "No",
        "Not sure",
        "Yes"
      )
    )) %>%
  dplyr::rename("Have station keys?" = have_keys)

have_keys_df <- data.frame(have_keys_df)
```

```{r have_keys}
plot(likert::likert(have_keys_df[, 1, drop = FALSE]), legend.position = "right")
```

## Last visit

```{r}
last_visit_df <- narc_fall_2021_mtn %>%
  dplyr::select(., last_visit) %>%
  dplyr::mutate(
    .,
    last_visit = factor(
      last_visit,
      levels = c(
        "Never visited",
        "Can't recall",
        "Sometime in 2019 or 2018",
        "Last Fall/Summer/Spring (2020)",
        "(Recently) Spring/Summer/Fall 2021"
      )
    )) %>%
  dplyr::rename("Last visit to the station" = last_visit)

last_visit_df <- data.frame(last_visit_df)
```

```{r last_station_visit}
plot(likert::likert(last_visit_df[, 1, drop = FALSE]), legend.position = "right")
```

Parsing `participated_in` and `would_participate_in` is going to take some work.

# Interpret

The largest percentage of respondents who have modest to high levels of interest were found for the following activities:

| Activity | Interested or Very Interested         | Occasional or regular experience |
|----------|:---------------------------------------:|:-----------------------------------------------:|
| APRS    | 61\%                                   | 31\% |
| FT8      | 57\%                                  | 29\% |
| fldigi  | 53\%                                   | 25\% |
| Digital voice | 48\%                             | 26\% |
| CW            | 38\%                             | 27\% |
| Winlink       | 33\%                             | 12\% |
| Satellite     | 32\%                             | 5\% |
| Contesting    | 28\%                             | 28\% |
| Packet        | 26\%                             | 15\% |
| ATV           | 23\%                             | 6\% |
| AREDN         | 20\%                             | 0\% |

More than half of respondents have keys and have visited in the last two years.